% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
% (c) 2019 Jumar Martin <jumar@jumart.in> https://jumart.in

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,10pt,draft]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
% \usepackage{draftwatermark}

% \SetWatermarkText{DRAFT}

\robustify\cftdotfill

%Use default sans-serif font
\renewcommand*\familydefault{\sfdefault} 


%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item[] \textbf{--} #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{3pt}
  {\setlength{\FrameSep}{\outerbordwidth}
    
\textbf{\large #1}
    
  }
}
\newcommand{\ressubheading}[5]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #3 -- #4\\
		\textit{#2} \\\\
\end{tabular*}\vspace{-6pt}
#5
}
\newcommand{\someitem}[2]{
	\textbf{#1}: #2
}
%-----------------------------------------------------------


\begin{document}


\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Jumar A. Martin} & \textbf{\today} \\
jumar@jumart.in | +1 (650) 407-9719 & Fourth-Year CS \& Econ Student
\end{tabular*}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\item[]
		\ressubheading{Elon University}{B.S. Computer Science, A.B. Economics}{2019}{2023}{\someitem{Relevant Coursework}{Data Mining \& Machine Learning, Programming Languages, Algorithm Analysis, Database Systems, Organization \& Architeture, Econometrics
}}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Technical Competencies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\item[]
		\someitem{Technical Competence}{Go, Swift 3+, Git, Python 3.x, Java 8+, PostgreSQL, Redis, \LaTeX}
	\item[]
		\someitem{Courseadvysr}{A service that was written to challenge—and now aiming to overtake—Elon University’s course search tool by providing better tools to decide which class to take. I host this service on a bare-metal SaaS server in a docker instance, \textbf{PostgreSQL} for the backend, \textbf{Golang} as the middleware, \textbf{Redis} to serve as a cache and broker authentication requests, and \textbf{ReactJS} as the presentation framework.}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Employment Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\item[]
		\ressubheading{Software Engineer Intern}{Cruise | Mapping}{Aug. 2022}{Present}{Serving as the ground-truth for the vehicles, the Mapping team spans both product and car side in providing navigation knowledge and intelligence.}
	\item[]
		\ressubheading{Software Engineer Intern}{Lyft | Driver Experience--Driver Productivity}{May 2022}{Aug. 2022}{Driver Experience aims to win driver preference by providing superior transparency and control. Amongst an 8.8\% increase in driver scheduled rides takeups by implementing an entrypoint in the unified schedule, I drove the prioritized implementation of bringing upfront pay swap notifications to parity with non-upfront pay and implemented new reasons to improve visibility into the reason a driver was swapped.}
	\item[]
		\ressubheading{Software Development Engineer Intern}{Amazon | Alexa Skills Kit}{Jan. 2022}{Apr. 2022}{As a member of the Vertical Kits team, I extended the Offers product to include the ability to reference by name instead of position, a highly requested feature by end users. This included designing a new schema for third-party partners to provide offer names and custom synonyms while also leveraging the Alexa Voice Service—an internal NLP product—to extend that synonyms list automatically.}
	\item[]
		\ressubheading{Software Engineer}{Celera Technologies}{Jun. 2021}{Jan. 2022}{Using \textbf{Python 3.9}, I architected automated systems that provide the ability to rapidly validate custom Integrated Circuits, generate mission-critical documentaiton for engineers and customers, and on average save 120 hours per week on once-manual tasks.}
	\item[]
		\ressubheading{Teaching Assistant}{Elon University}{Aug. 2021}{Dec. 2021}{Served as the only TA for 118 students in the introductory Computer Science course.}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Employment Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
	\item[]
		\ressubheading{President}{Elon Society of Computing}{Apr. 2019}{Jan. 2022}{Serving as President of ESC, I transferred ownership of Courseadvysr to the newly-found ESC Student Development Team and continually led that team in developing new features and services, recreated the event planning to allow students to easily follow a Research or Real World-focused track, and expanded ESC’s reach as a strong department-affiliated organization.}
\end{itemize}



\end{document}
